---
title: "CIVL 443 Geoenvironmental Design – CEAB GA Report"
author: "Jake Kaupp"
date: "May 8, 2015"
output:
  pdf_document: default
  html_document:
    theme:
    - cosmo
---

```{r, echo=FALSE, warning = FALSE, message = FALSE}
source("/Users/Jake/ownCloud/Projects/R/Projects/EGAD/civl special.R")
```


This is a preliminary report for CIVL 443, summarizing the 2014/2015 Winter Semester.

---

##

Indicator      | Description | Where Assessed | Assessment Method |       
---------------|-----------------------------------------------------------------------------------------|-----------------|--------|
CIVL-4-PA-Gx   | Calculate one-dimensional advective flow through natural and engineered layered systems | Task 4 | Rubric |
CIVL-4-ET-Gx+1 | Calculate contaminant impact on receptor aquifer from waste containment facility | Task 4 | Rubric |
CIVL-4-IN-Gx+2 | Construct geologic site model by designing a site investigation and interpreting results| Task 2a, 2b, 2c | Rubric |
CIVL-4-DE-Gx+3 | Design a barrier system for a waste containment facility that meets Provincial environmental regulations and satisfies current and anticipated needs of a hypothetical municipality | Task 5 | Rubric


##Student Performance on Mapped Inidicators

###Graduate Attribute: Problem Analysis

```{r, echo=FALSE}
plot.title = 'CIVL-4-PA-Gx'
plot.subtitle = 'Calculate one-dimensional advective flow through natural and engineered layered systems'

ggplot(civl.4.pa.gx, aes(x = `CIVL-4-PA-Gx`)) + 
  geom_histogram(aes(fill=`CIVL-4-PA-Gx`)) + 
  ylab("Count") + 
  ggtitle(bquote(atop(.(plot.title), atop(italic(.(plot.subtitle)), "")))) +
  xlab("Performance") + 
  xlim(civl.levels) +
  theme_hc() +
  theme(legend.position="none") +
  theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0)) +
  theme(text = element_text(size=12))
```

### Graduate Attribute: Engineering Tools

```{r, echo=FALSE}
plot.title = 'CIVL-4-ET-Gx+1'
plot.subtitle = 'Calculate contaminant impact on receptor aquifer from waste containment facility'

ggplot(civl.4.et.gx1, aes(x = `CIVL-4-ET-Gx+1`)) + 
  geom_histogram(aes(fill=`CIVL-4-ET-Gx+1`)) + 
  ylab("Count") + 
  ggtitle(bquote(atop(.(plot.title), atop(italic(.(plot.subtitle)), "")))) +
  xlab("Performance") + 
  xlim(civl.levels) +
  theme_hc() +
  theme(legend.position="none") +
  theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0)) +
  theme(text = element_text(size=12))
```

### Graduate Attribute: Investigation

Student peformance on this indicator was calculated by calculating the mean score from each of the Task 2a, Task 2b and Task 2c rubrics.

```{r, echo=FALSE}
plot.title = 'CIVL-4-IN-Gx+2'
plot.subtitle = 'Calculate contaminant impact on receptor aquifer from waste containment facility'

ggplot(civl.4.in.gx2, aes(x = `CIVL-4-IN-Gx2`)) + 
  geom_histogram(aes(fill=`CIVL-4-IN-Gx2`)) + 
  ylab("Count") + 
  ggtitle(bquote(atop(.(plot.title), atop(italic(.(plot.subtitle)), "")))) +
  xlab("Performance") + 
  xlim(civl.levels) +
  theme_hc() +
  theme(legend.position="none") +
  theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0)) +
  theme(text = element_text(size=12))
```

The development of this indicator over time would be:

```{r, echo=FALSE}
plot.title = 'CIVL-4-IN-Gx2 Over time'
plot.subtitle = 'Calculate contaminant impact on receptor aquifer from waste containment facility'

ggplot(time.gax2, aes(x = indicator)) + 
  geom_histogram(aes(fill= indicator)) + 
  facet_wrap(~rubric, scales = "fixed", ncol=3) +
  ylab("Count") + 
  ggtitle(bquote(atop(.(plot.title), atop(italic(.(plot.subtitle)), "")))) +
  xlab("Performance") + 
  xlim(civl.levels) +
  theme_hc() +
  theme(legend.position="none") +
  theme(axis.text.x = element_text(angle = 90, hjust = 0, vjust = 0)) +
  theme(text = element_text(size=12))
```

### Graduate Attribute: Design

The results for this assessment could not be calculated due to 1:26 ratio for measurement with the majority of the measurement aspects having differing levels of performance.

