---
title: "MECH Gradaute Attribute Report"
author: "Jake Kaupp"
date: "May 22nd, 2015"
output:
  pdf_document: default
  html_document:
    number_sections: yes
    theme: journal
---
```{r options, echo=FALSE, warning = FALSE, message = FALSE}
source("/Users/Jake/ownCloud/Projects/R/Projects/EGAD/R/MECH Analysis.R")
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Introduction
***

The following is a program-level report on the Graduate Attribute Assessment and Continuous Improvement Process efforts in the Deparment of Mechanical and Materials Engineering.  It should help provide a view into the performance of each cohort and potentially reveal some aspects of the program that could be considered for future improvement.  

_Please note: The structure of the report is a work in progress, and any constructive feedback would be appreciated._

***

## MECH Department Overview
The following figure presents a dashboard-style view of the mechanical program from the an assessment perspective, contrasting the current and previous assessment yeras. The dashboard is vertically panneled by program year and each dot represents the aggregate student performance of a specific indicator.

```{r dashboard view, tidy = TRUE, fig.width = 15, fig.height = 10, fig.cap = "Figure 1: MECH Program Overview"}
m.mech %>%
  p.ypc()
```


## Second Year
***
### Knowledge Base
```{r MECH-2-KB, fig.width = 10, fig.height = 12, fig.cap = "Figure 2: Knowledge Base: Second Year MECH"}
one <- m.mech %>% 
  filter(attribute == "KB", program_year == 2, academic_year=="2013-2014")

two <- m.mech %>% 
  filter(attribute == "KB", program_year == 2, academic_year=="2014-2015")

m.mech %>%
  filter(attribute == "KB", program_year == 2) %>%
  filter(.,!grepl("MECH-", description)) %>%
  filter(indicator %in% intersect(one$indicator,two$indicator)) %>% 
  ga.hist()
```

### Investigation
_Note that there is no assessment data for this attribute from `r unique(prev.mech$ACADEMIC_YEAR)`_

```{r MECH-2-IN, fig.width = 10, fig.height = 6, fig.cap = "Figure 3: Investigtion: Second Year MECH"}
m.mech %>%
  filter(attribute == "IN", program_year == 2) %>%
  ga.hist()
```

### Communication
_Note that there is no assessment data for this attribute from `r unique(prev.mech$ACADEMIC_YEAR)`_

```{r MECH-2-CO, fig.width = 10, fig.height = 5, fig.cap = "Figure 4: Communication Second Year MECH"}
m.mech %>%
  filter(attribute == "CO", program_year == 2) %>%
  filter(.,!grepl("MECH-", description)) %>%
  ga.hist()
```

***

## Third Year
***

### Knowledge Base 
```{r MECH-3-KB, fig.width = 10, fig.height = 12, fig.cap = "Figure 5: Knowledge Base: Third Year MECH"}

one <- m.mech %>% 
  filter(attribute == "KB", program_year == 3, academic_year=="2013-2014")

two <- m.mech %>% 
  filter(attribute == "KB", program_year == 3, academic_year=="2014-2015")


m.mech %>%
  filter(attribute == "KB", program_year == 3) %>%
  filter(.,!grepl("MECH-", description)) %>% 
  filter(indicator %in% intersect(one$indicator,two$indicator)) %>% 
  ga.hist()
```

### Investigation 
```{r MECH-3-IN, fig.width = 10, fig.height = 5, fig.cap = "Figure 6: Investigation: Third Year MECH"}
m.mech %>% 
  filter(attribute == "IN", program_year == 3) %>% 
  filter(.,!grepl("MECH-", description)) %>% 
  ga.hist()
```

### Design
```{r MECH-3-DE, fig.width = 10, fig.height = 5, fig.cap = "Figure 7: Design: Third Year MECH"}
one <- m.mech %>% 
  filter(attribute == "DE", program_year == 3, academic_year=="2013-2014")

two <- m.mech %>% 
  filter(attribute == "DE", program_year == 3, academic_year=="2014-2015")

m.mech %>%
  filter(attribute == "DE", program_year == 3) %>%
  filter(indicator %in% intersect(one$indicator,two$indicator)) %>% 
  ga.hist()
```

### Communication
```{r MECH-3-CO, fig.width = 10, fig.height = 5, fig.cap = "Figure 8: Communication: Third Year MECH"}
if(m.mech %>%
   filter(attribute == "CO", program_year == 3) %>%
   tally <=0) {
   sprintf("There are no records for this attribute")
   } else{
   m.mech %>%
   filter(attribute == "CO", program_year == 3) %>%
   filter(.,!grepl("MECH-", description)) %>%
   ga.hist()
   }
```

### Engineering Tools
```{r MECH-3-ET, fig.width = 10, fig.height = 5, fig.cap = "Figure 9: Engineering Tools: Third Year MECH"}
if(m.mech %>%
   filter(attribute == "ET", program_year == 3) %>%
   tally <=0) {
   sprintf("There are no records for this attribute")
   } else{
   m.mech %>%
   filter(attribute == "ET", program_year == 3) %>%
   filter(.,!grepl("MECH-", description)) %>%
   ga.hist()
   }
```

### Professionalism
```{r MECH-3-PR, fig.width = 10, fig.height = 5, fig.cap = "Figure 10: Professionalism: Third Year MECH"}
if(m.mech %>%
   filter(attribute == "PR", program_year == 3) %>%
   tally <=0) {
   sprintf("There are no records for this attribute")
   } else{
   m.mech %>%
   filter(attribute == "PR", program_year == 3) %>%
   filter(.,!grepl("MECH-", description)) %>%
   ga.hist()
   }
```

### Teamwork
```{r MECH-3-TW, fig.width = 10, fig.height = 5, fig.cap = "Figure 11: Teamwork: Third Year MECH"}
if(m.mech %>%
   filter(attribute == "TW", program_year == 3) %>%
   tally <=0) {
   sprintf("There are no records for this attribute")
   } else{
   m.mech %>%
   filter(attribute == "TW", program_year == 3) %>%
   filter(.,!grepl("MECH-", description)) %>%
   ga.hist()
   }
```

### Lifelong Learning
```{r MECH-3-LL, fig.width = 10, fig.height = 5, fig.cap = "Figure 12: Lifelong Learning: Third Year MECH"}
if(m.mech %>%
   filter(attribute == "TW", program_year == 3) %>%
   tally <=0) {
   sprintf("There are no records for this attribute")
   } else{
   m.mech %>%
   filter(attribute == "TW", program_year == 3) %>%
   filter(.,!grepl("MECH-", description)) %>%
   ga.hist()
   }
```

***

## Fourth Year
***
### Problem Analysis
```{r MECH-4-PA, fig.width = 10, fig.height = 5, fig.cap = "Figure 13: Problem Analysis: Fourth Year MECH"}
if(m.mech %>%
   filter(attribute == "PA", program_year == 4) %>%
   tally <=0) {
   sprintf("There are no records for this attribute")
   } else{
   m.mech %>%
   filter(attribute == "PA", program_year == 4) %>%
   filter(.,!grepl("MECH-", description)) %>%
   ga.hist()
   }
```

### Design
```{r MECH-4-DE, fig.width = 10, fig.height = 5, fig.cap = "Figure 14: Design: Fourth Year MECH"}
if(m.mech %>%
   filter(attribute == "DE", program_year == 4) %>%
   tally <=0) {
   sprintf("There are no records for this attribute")
   } else{
   m.mech %>%
   filter(attribute == "DE", program_year == 4) %>%
   filter(.,!grepl("MECH-", description)) %>%
   ga.hist()
   }
```

### Engineering Tools
```{r MECH-4-ET, fig.width = 10, fig.height = 5, fig.cap = "Figure 15: Engineering Tools: Fourth Year MECH"}
if(m.mech %>%
   filter(attribute == "ET", program_year == 4) %>%
   tally <=0) {
   sprintf("There are no records for this attribute")
   } else{
   m.mech %>%
   filter(attribute == "ET", program_year == 4) %>%
   filter(.,!grepl("MECH-", description)) %>%
   ga.hist()
   }
```

### Teamwork
```{r MECH-4-TW, fig.width = 10, fig.height = 5, fig.cap = "Figure 16: Teamwork: Fourth Year MECH"}
if(m.mech %>%
   filter(attribute == "TW", program_year == 4) %>%
   tally <=0) {
   sprintf("There are no records for this attribute")
   } else{
   m.mech %>%
   filter(attribute == "TW", program_year == 4) %>%
   filter(.,!grepl("MECH-", description)) %>%
   ga.hist()
   }
```

### Communication
```{r MECH-4-CO, fig.width = 10, fig.height = 5, fig.cap = "Figure 17: Communication: Fourth Year MECH"}
if(m.mech %>%
   filter(attribute == "CO", program_year == 4) %>%
   tally <=0) {
   sprintf("There are no records for this attribute")
   } else{
   m.mech %>%
   filter(attribute == "CO", program_year == 4) %>%
   filter(.,!grepl("MECH-", description)) %>%
   ga.hist()
   }
```

### Professionalism
```{r MECH-4-PR, fig.width = 10, fig.height = 5, fig.cap = "Figure 18: Professionalism: Fourth Year MECH"}
if(m.mech %>%
   filter(attribute == "PR", program_year == 4) %>%
   tally <=0) {
   sprintf("There are no records for this attribute")
   } else{
   m.mech %>%
   filter(attribute == "PR", program_year == 4) %>%
   filter(.,!grepl("MECH-", description)) %>%
   ga.hist()
   }
```

### Impact of Engineering
```{r MECH-4-IM, fig.width = 10, fig.height = 5, fig.cap = "Figure 19: Impact of Engineering: Fourth Year MECH"}
if(m.mech %>%
   filter(attribute == "IM", program_year == 4) %>%
   tally <=0) {
   sprintf("There are no records for this attribute")
   } else{
   m.mech %>%
   filter(attribute == "IM", program_year == 4) %>%
   filter(.,!grepl("MECH-", description)) %>%
   ga.hist()
   }
```

### Economics & Project Management
```{r MECH-4-EC, fig.width = 10, fig.height = 5, fig.cap = "Figure 20: Economics & Project Management: Fourth Year MECH"}
if(m.mech %>%
   filter(attribute == "EC", program_year == 4) %>%
   tally <=0) {
   sprintf("There are no records for this attribute")
   } else{
   m.mech %>%
   filter(attribute == "EC", program_year == 4) %>%
   filter(.,!grepl("MECH-", description)) %>%
   ga.hist()
   }
```

### Lifelong Learning
```{r MECH-4-LL, fig.width = 10, fig.height = 5, fig.cap = "Figure 21: Lifelong Learning : Fourth Year MECH"}
if(m.mech %>%
   filter(attribute == "LL", program_year == 4) %>%
   tally <=0) {
   sprintf("There are no records for this attribute")
   } else{
   m.mech %>%
   filter(attribute == "LL", program_year == 4) %>%
   filter(.,!grepl("MECH-", description)) %>%
   ga.hist()
   }
```

